Whole Genome Resequencing for Population Genomics

### 2022-11-04 DGE_comparison_v2.Rmd
added cache = TRUE to some of the tutorials that take a long time to render. doing this to try to make it easier & quicker to re-render the website and update the nav bar

```{r setup, include = FALSE}
# should remove from Rmd
# Set root directory
#knitr::opts_knit$set(root.dir = '~/Documents/GitHub/DGE_comparison/')

>>>>

```{r setup, include = FALSE}
# should remove from Rmd
# Set root directory
#knitr::opts_knit$set(root.dir = '~/Documents/GitHub/DGE_comparison/')
knitr::opts_chunk$set(echo = TRUE)

### 2022-11-04 WGS_intro.Rmd
testing an attempt to consolidate all materials to this website rather than linking to another git repo, starting with the first tutorial in lcWGS
added cache = TRUE to some of the tutorials that take a long time to render. doing this to try to make it easier & quicker to re-render the website and update the nav bar

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
knitr::opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(knitcitations)
knitr::opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```
